SatNOGS: Satellite~Networked~Open~Ground~Station

### 2015-08-24 paper.tex
use IEEE 2-column format
add Makefile, pdflatex setup

\documentclass{article}

\title{SatNOGS: Satellite Networked Open Ground Station}
\author{Dan White}

@@

\section{Introduction}

\section{}

>>>>

\documentclass[conference]{IEEEtran}

\usepackage[]{hyperref}

\hypersetup{
    letterpaper,
    colorlinks,
    urlcolor=blue,
    linkcolor=darkblue,
    citecolor=darkblue,
}

\author{
    \IEEEauthorblockN{Daniel J. White\IEEEauthorrefmark{1},
        SatNOGS Developers\IEEEauthorrefmark{2}}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Valparaiso University, \href{mailto:dan.white@valpo.edu}{dan.white@valpo.edu}}
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Libre Space Foundation,
    \href{mailto:info@satnogs.org}{info@satnogs.org}}

}

\title{SatNOGS: Satellite~Networked~Open~Ground~Station}

%TODO: add other authors

@@

\section{Introduction}
FOo

\section{Network}

\section{Database}

\section{Client}

\section{Ground Station}

\section{Conclusion}
